---
title: "Practical Example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Practical Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, setup, warning = FALSE, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(uniset)
to <- path.expand("~/desktop")
dsource <- paste0(path.package("uniset"), "/examples/dogPack")
file.copy(dsource, to, recursive = TRUE) 
setupFunc <- "dogPack_demo_setup" # the name of the setup-function in our example
path <- paste0(to, "/dogPack")
uniset_copyFilesToPackage(path, setupFunc)
```

In the following examples we will obtain the value from the key 'favouriteColor' from the file 'dogPack.settings.R'.

## Initialise Settings File System

Assuming you copied or moved the required files as [described before](https://bpollner.github.io/uniset/articles/uniset.html), open the RStudio project file in the folder 'temdir()/dogPack', build and install the package.

```{r}
# done here for the sake of creating the vignette-output
to <- path.expand("~/desktop")
ptp <- paste0(to, "/dogPack")
devtools::document(ptp, roclets = c('rd', 'collate', 'namespace'), quiet = TRUE)
devtools::install(ptp)
```

### Define Location of settings.R File {#define-location}

To define the location of the user-defined settings.R file, use the `uniset` setup function `uniset_setup()`:

```{r}
library(dogPack)
dogPack_test_targetPackageParams() # gives a printout of the target package parameters
dogPack_demo_setup(where=to) # will place the settings-home folder on the desktop
```

`dogPack_demo_setup` contains the `uniset` function `uniset_setup()`.

This has to be done **only once** by the user of the target package. You probably have to **restart R** now for the changes in the environment variable in your .Renviron file to become effective.

## Getting Values

By now everything should be ready and set up. You can look at the settings via

```{r}
stn <- dogPack_demo_updateSettings()
str(stn)
```

Use the function `getstn` defined in package 'dogPack' to directly obtain the settings list -- see the example code in `dogPack_demo_autoUpS` and `dogPack_demo_tellFavouriteColor` in the example folder copied previously.

`getstn` was customized by package `uniset` at the time of creating the four required files and is located in the file 'uniset_functions.R' in 'dogPack/R'.

```{r}
dogPack_demo_tellFavouriteColor()
# contains the function 'getstn'
```

Now open the file 'dogPack_settings.R' in the folder 'dogPack_SH' that was created during setup, and change the value of the key 'favouriteColor' to "orange". After that, call

``` r
dogPack_demo_tellFavouriteColor() # should be "orange" now
#> "orange"
```

Every time one of the functions `uniset_updateSettings()`, `uniset_autoUpS()` or `uniset_getstn()` is called from **within the target package**, the key = value pairs from the user-defined settings.R file are sourced and returned.\
The location of the user-defined settings.R file can be defined via `uniset_autoUpS()` as [shown above](#define-location).

------------------------------------------------------------------------

## Adding / deleting keys

If you are the developer of package `dogPack`, at some time after you published `dogPack` you might want to add keys to or delete from the settings file.

### Adding Keys

Do that now: Add e.g. a new 'key=value,' pair (do not forget the comma ',') anywhere in the settings-file **in the folder 'inst' of `dogPack`**, and re-install `dogPack`. Or, as an alternative shortcut for this demonstration, go to root of the *installed* `dogPack` package at

```r
path.package("dogPack")
```

and there simply modify the file 'dogPack_settings.R' (add a key called "someNewKey").

Now the **user** of `dogPack` calls a function that includes the auto-update function `uniset::uniset_autoUpS()`:

``` r
dogPack_demo_No_autoUpS()
#> My favourite color is: orange
#> # user defined settings.R file is NOT modified
dogPack_demo_autoUpS()
#>
#> The following 1 key was added to the settings-file 'dogPack_settings.R' in 
#> '/Users/bernhard/desktop/dogPack_SH':
#>  someNewKey
#> 
#> My favourite color is: orange
```

The **user** of `dogPack` will then have the new key added to the local file 'dogPack_settings.R' in the folder 'dogPack_SH' in the settings-home directory.

### Deleting Keys

The same is true for deleting keys: again, open the file 'dogPack_settings.R' in the root of `path.package("dogPack")` and delete the previously added key. Now the **user** of `dogPack` calls again a function that includes the auto-update function `uniset::uniset_autoUpS()`:

``` r
dogPack_demo_No_autoUpS()
#> My favourite color is: orange
#> # user defined settings.R file is NOT modified
dogPack_demo_autoUpS()
#> 
#> The following 1 key was deleted from the settings-file 'dogPack_settings.R' in 
#> '/Users/bernhard/desktop/dogPack_SH':
#>  someNewKey
#>  
#> My favourite color is: orange
```

The surplus key was deleted from the local file 'dogPack_settings.R'.

Practically, it makes sense to include the auto-update in every function that the user of the target package can call, and to not include it in all the other functions.

You might want to read the code in the practical examples in the [previously copied file](https://bpollner.github.io/uniset/articles/uniset.html#set-up-example) `dogPack/R/dogPackFunc.R`, as they fully illustrate the usage of the functions exposed by `uniset` in the target package.

Enjoy !
