---
title: "uniset"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{uniset}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Package `uniset` provides an easily accessible, user-friendly text file as settings-file for your R-package.

## Description

Package `uniset` enables any package (the 'target package') to provide its users an easily accessible, user-friendly and human readable text file where key=value pairs (used by functions defined in the target package) can be saved.

This settings file lives in a location defined by the user of the target package, and its user-defined values remain unchanged even when the author of the target package is introducing or deleting keys, or when the target package is updated or re-installed.

In order to enable the target package to make use of the functionality offered by package `uniset`, three files have to be exported by `uniset` and be placed into the target package.

## Installation

Install release version from CRAN via

``` r
install.packages("uniset")
```

Or download from github:

``` r
install_github(repo="bpollner/uniset", ref="master")
```

------------------------------------------------------------------------

## Set up example {#set-up-example}

We assume that we want to enable a package called `dogPack` to use the dynamic settings file provided by `uniset`. In this example, `dogPack` is the target package, and we want it to live at `~/desktop`. First copy the example folder `dogPack` to your desktop:

```{r}
library(uniset)
to <- path.expand("~/desktop")
dsource <- paste0(path.package("uniset"), "/examples/dogPack")
file.copy(dsource, to, recursive = TRUE) 
```

## Generate Files

There are two ways to set up a target package (in our example the package called `dogPack`) to make use of `uniset`:

### **A) Export and Move Files**

The package name, the name of the setup-function and a location have to be specified, then a call to `uniset_getFiles()` creates a folder containing the three required files:

```{r}
setupFunc <- "dogPack_demo_setup" # the name of the setup-function in our example
uniset_getFiles("dogPack", setupFunc, to)
```

Move files:

-   'dogPack_settings.R' into the 'inst' folder (create one if not already done) of `dogPack`.

-   'uniset_globals' and 'uniset_functions.R' into the 'R' folder of `dogPack`.

### **B) Write files directly to target package**

A call to `uniset_copyFilesToPackage()` copies the three required files directly into the target package -- called `dogPack` in our example.

```{r}
path <- paste0(to, "/dogPack")
setupFunc <- "dogPack_demo_setup" # the name of the setup-function in our example
uniset_copyFilesToPackage(path, setupFunc)
```

Please review the file 'dogPackFunc.R' in the folder 'dogPack/R' that was copied to `tempdir()` and look at the code of the practical examples that will be executed below.

Go on and read the [extended description](https://bpollner.github.io/uniset/articles/description.html) to deepen your understanding of how `uniset` works.
